\vspace{-1.3cm} \textmd{\normalsize{Project description}}\\ Parallelization of the Probabilistic Roadmap Method with GPU Acceleration

### 2016-03-28 paper/paper.tex
robot kernel chapter...

@@

The indicator function is implemented in a vectorized way as an CUDA kernel, which means that, given set of states $q^1,..,q^N$, the indicator function is evaluated for each state by one CUDA thread. Therefore, the kinematics and collision algorithm have been implemented as device code for the use in the kernel.

@@

\subsection{Chung-Wang Collision Algorithm}

\begin{lstlisting}
__host__ __device__ int seperating_vector_algorithm(const polytope4& P, const polytope4& Q, 
													const trafo4& tp, const trafo4& tq);
\end{lstlisting}

@@

- the indicator function gets:

	- polytopes in coordinate frames

	- data, which pairs must be tested

	- q

  and computes if for any pair $(i,j)$ the polytopes $P_i, P_j$ collide in the world frame

- implements the indicator function for multiple requests parallely:

- input: lists qstart, qend

- output: res

$res[i] = 0$ if indicator(q) == 0 for all q in $[ qstart[i], qend[i] ]_deltaq$

	!= 0 else

@@

>>>>

\usepackage[ruled]{algorithm2e}

@@

The indicator function is implemented in a vectorized way as an CUDA kernel, which means that, given set of states $q^1,..,q^M$, the indicator function is evaluated for each state by one CUDA thread. Therefore, the kinematics and collision algorithm have been implemented as device code for the use in the kernel.

@@

\subsection{Chung-Wang Collision Algorithm}
The indicator function is implemented in a compressed way
\begin{lstlisting}
__host__ __device__ int seperating_vector_algorithm(const polytope4& P, const polytope4& Q, 
													const trafo4& tp, const trafo4& tq);
\end{lstlisting}

@@

\begin{lstlisting}
int indicator2(const float* qs, const float* qe, int *res, const int N, const int offset);
\end{lstlisting}
It gets as input a list of border points $q_{start}^j, q_{end}^j, j=0,...,N$. This are the nodes passed by the PRMSolver. The indicator function checks now for each pair, if on the line in between the indicator function is always 0.
\begin{equation}
	res[j]=\begin{cases}
		0	&\text{if $I(q)=0$ f.a. $q \in \left[qs[j], qe[j]\right]_{\Delta q}$} \\
		1	&else
	\end{cases}
\end{equation}
The border points are stored in structures of arrays.
\begin{equation}
\begin{aligned}
	q_{start}^j &= \left(qs[j],qs[j+\text{offset}],...,qs[j+(d-1)*\text{offset}]\right)^T
	q_{end}^j &= \left(qe[j],qe[j+\text{offset}],...,qe[j+(d-1)*\text{offset}]\right)^T
\end{aligned}
\end{equation}

\begin{algorithm}
	\KwData{qs, qe, N, offset}
	\KwResult{res}
	compute distances $d_j = \abs{q_{end}^j - q_{start}^j}$ \;
	testnum[j] = $d_j/{\Delta q}$: number of threads for each line \;
	testpos[j] = thread displacements \;
	reset res \;
	call kernel \;
	\caption{Host indicator function}
\end{algorithm}

\begin{algorithm}
	\KwData{arrays qs, qe, testpos, testnum and threadindex}
	\KwResult{res}
	compute associated edge number $j$, defined by $testpos[j] \leq threadindex \le testpos[j]+testnum[j]$ \;
	$c = (threadindex - testpos[j]) / (testnum[k]-1) $ \;
	$q=c q_{start}^j + (1-c) q_{end}^j $ \;
	calculate robot kinematics $T_0(q), ..., T_d(q) $\;
	$res_{tmp} = 0; $ \;
	\For{all registered pairs pairs of polytopes $P, Q$}{
		$res_{tmp}=seperating\_vector\_algorithm(P, T_{i_P}, Q, T_{i_Q})$ \;
		\If{$res_{tmp} \neq 0$}{
			$res[j]=res_{tmp}$ \;
			break \;
		}
	}
	\caption{Robot kernel: code for one thread}
\end{algorithm}

@@

In order to overlap computation time of GPU and CPU, an asynchronous version of the indicator function was written. Here the function is split in everything until the kernel launch and a wait function, which waits until the kernel finishes and recieves the result data. The implementation allows also overlapping of multiple requests, for example two calls of the launch function and after this the two waiting calls. With this it is possible the full computation time of the GPU.

\begin{lstlisting}
int indicator2_async(const float* qs, const float* qe, int *res, 
					 const int N, const int offset, int &request);
int indicator2_async_wait(int request);
\end{lstlisting}
